Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2020-05-04 PaperMagneticProfiles_JBSMSE.tex
Clarify description of figure of comparison between profiles.
Explain why cooling capacity is non-linear with utilization.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{Fig6-profiles_rc_and_flow_instantaneous}
  \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
  \label{fig:cos-inst-60}
\end{figure}

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations. The horizontal axis shows the average field value during the high field region. The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.  As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.

@@

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{Fig6-profiles_rc_and_flow_instantaneous}
  \caption{Rectified cosine magnetic profile (solid lines) and the instantaneous flow profile  with blow fraction of \SI{60}{\percent} (dashed lines)}
  \label{fig:cos-inst-60}
\end{figure}

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations. The horizontal axis shows the average field value during the high field region. The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance; as demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss. Analyzing points of different profiles of constant utilization (which should result in the same regenerator effectiveness), 
 for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile. This is the result of the fluid being able to cool down to lower temperatures during the low-field cycle, since the cosine profile cannot maintain the field as low as the instantaneous profile (cf. \autoref{fig:comparison-methods-profiles}), even with the reduction of blow fraction.

@@

Also noticeable in \autoref{fig:cos_ins} is the non-linear relationship  between cooling capacity and utilization. For instance, for the ``RC'' profile at the highest magnetic field, the cooling capacity increases when the utilization grows from 0.2 to 0.6, but then return to the same levels with a further increase of utilization to 1.0. Since the frequency is constant for \autoref{fig:cos_ins}, increasing utilization means increasing the mass flow rate; initially, this results in higher heat transfer rates due to higher Nusselt numbers, but further increase reduce the effectiveness and amplify viscous dissipation, to the point where the cooling capacity is null for certain points with the highest utilization.
